Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-29 ms.tex
more on dipole fits

@@

With $p$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
In the context of Equation \ref{equ:dip}, $\nu_i \in$  
\{100, 143, 217, 353, 545\} GHz. $\mathcal{D}$ is a scaling of the Solar dipole
pattern oriented toward $(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit 
amplitude. Because $\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we 
have an overconstrained linear model with three parameters: a, b, and c. $a$ 
represents the slope of \PLANCK~band $\nu_i$ GHz versus \PLANCK~857 GHz 
assuming they are linearly correlated. $b$ represents the scaling of the Solar 
dipole that makes the 857 GHz vs. \PLANCK~band $\nu_i$ correlation most tightly
linear, and $c$ represents the constant offset necessary to make the zero level
 of the band $\nu_i$ map consistent with that of the 857 GHz map. Performing a 
linear least squares fit with uniform weights and iterative outlier rejection, 
we find $a=4.33\times10^{-5}\ K/(MJy/sr)$, $b=-1.40\times10^{-5}\ K$, and 
$c=8.12\times10^{-5}\ K$. Note that $b$ represents 0.42\% of the Solar dipole 
amplitude, which is within the calibration uncertainty of the \PLANCK~217 GHz 
band. Figure \ref{fig:scatter} shows scatterplots of the 857 GHz versus 217 
GHz correlation before and after correcting for our best-fit offset and dipole 
residual. Not only is the improved correlation striking in this scatterplot, 
but the residual dipole also appears visually well-corrected in the 217 GHz 
map itself. Before performing thermal dust fits, we therefore subtract $c$ and 
$b\mathcal{D}$ from the 217 GHz map.

%in above paragraph, clarify what dipole means i.e. in what direction
% on sky it's oriented

%mention the special case of 100 GHz w/ quadrupole term ... do i need
% another equation ?

>>>>

% should really change labels to have **script** I to be consistent with the
% notation used in the text

@@

With $p$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
In the context of Equation \ref{equ:dip}, $\nu_i \in$  
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: a, b, and c. $a$ represents
the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz assuming 
they are linearly related. $b$ represents the scaling of the Solar dipole that 
makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. 
$c$ represents the constant offset necessary to make the zero level of the 
band $\nu_i$ map consistent with that of the 857 GHz map. For each band
$\nu_i$, we obtain estimates of $a$, $b$, and $c$ by performing a linear least 
squares fit with uniform weights and iterative outlier rejection. Figure 
\ref{fig:dip} shows scatterplots of the band $\nu_i$ versus 857 GHz correlation
before and after correcting for the best-fit offset and residual dipole, for
each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the tightened 
correlations striking in these scatterplots, but the residual dipole 
subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
themselves. Before performing thermal dust fits, we therefore subtract the 
best-fit $c$ and $b\mathcal{D}$ from each band $\nu_i$ map. The best-fit
offsets and residual dipole amplitudes are listed in Table \ref{table:offs}.

% mention the special case of 100 GHz w/ quadrupole term !!!!!!
% do i need another equation ?
